Ms 1

### 2017-10-13 ms1/ms1_display.Rmd
ms1: better dx

# compute risk ratios
pde_inapprop_trends = read_tsv('tables/pde_inapprop_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_inapprop_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p)
  # now estimate is adjusted change in INappropriate prescribing

adjusted_changes_firstfill = read_tsv('tables/model_abx_firstfill.tsv') %>%
  rename(antibiotic=name) %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  model_ci() %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>%
  mutate(antibiotic=fct_inorder(antibiotic),
         antibiotic=fct_relevel(antibiotic, 'overall', after=Inf))

ggplot(adjusted_changes_firstfill, aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_hline(yintercept=0) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  geom_point(dat=pde_approp_trends, color='blue', shape=1) +
  geom_errorbar(dat=pde_approp_trends, width=0.25, color='blue') +
  coord_flip() +
  xlab('') +
  ylab('adjusted change from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 35), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_classic() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r pde_approp_trends_table}
pde_approp_trends %>% kable
```

@@

And, to be more careful, I show the answer to a similar question but using a regression to correct for covariates:

```{r pde_approp_trends}
read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  #select(antibiotic, estimate, p.value) %>%
  mult_est(3) %>%
  model_ci() %>%
  mutate(antibiotic=factor(antibiotic, levels=c('overall', top_abx))) %>%
  arrange(antibiotic) %>%
  select(antibiotic, pct_change, ci_low, ci_high, p.value) %>%
  kable
```

>>>>

adjusted_changes_firstfill = read_tsv('tables/model_abx_firstfill.tsv') %>%
  rename(antibiotic=name) %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  model_ci() %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>%
  mutate(antibiotic=fct_relevel(fct_inorder(factor(antibiotic)), 'overall', after=Inf))

# compute risk ratios
pde_inapprop_trends = read_tsv('tables/pde_inapprop_trends.tsv') %>%
  filter(term=='year', antibiotic != 'Other') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_inapprop_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents
  mutate_at(vars(estimate, ci_low, ci_high), function(x) (x - 1)*100) %>%
  select(antibiotic, model, pct_change=estimate, ci_low, ci_high, adj.p) %>%
  # now estimate is adjusted change in INappropriate prescribing
  mutate(antibiotic=factor(antibiotic, levels=levels(adjusted_changes_firstfill$antibiotic), ordered=TRUE))

ggplot(adjusted_changes_firstfill, aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high, color=model)) +
  geom_hline(yintercept=0) + 
  geom_bar(aes(color=NULL), stat='identity', fill=NA, color='black') +
  geom_errorbar(aes(color=NULL), width=0.5) +
  geom_point(dat=pde_inapprop_trends, shape=1) +
  geom_errorbar(dat=pde_inapprop_trends, width=0.25) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 35), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_classic() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r pde_approp_trends_table}
pde_inapprop_trends %>% kable
```

@@
